Graph Exploration and Search

### 2017-11-12 exploratory.tex
Finished reformulation

\noindent One of the earliest attempts to bring examples as a query method is query-by-example~\citep{zloof1975query}.
The main idea was to help the user in the query formulation, allowing her to specify the shape of the results in terms of templates for tuples, i.e., examples.
Query-by-example has been lately revisited, and the use of examples have found application in graph data as well. 
The definition of example has transformed from a mere template to the representative of the intended results the user would like to have.
\emph{Examples} for a graph $G = (V,E)$ can be either \emph{set of nodes} $Q \subseteq V$, \emph{tuple} of nodes $(v_1, ..., v_n) \in V^n$, or \emph{subgraphs} $Q \subseteq G$, where with an abuse of notation $\subseteq$ indicates both set and structural inclusion.

\eetitle{Set of nodes as examples.} Several analyses can be performed when a set of examples nodes $Q\subseteq V$ is provided; this includes the discovery of dense graph regions~\citep{gionis2015bump,ruchansky2015minimum}, central nodes~\citep{tong2006center}, communities~\citep{staudt2014detecting,perozzi2014focused}.%, and targeted graph summarization~\citep{zhang2010discovery}. 
Discrepancy maximization in graphs~\citep{gionis2015bump} aims at finding a connected subgraph $G' = (V', E'), G' \subseteq G$ that maximizes the discrepancy $\delta(G'){=}\alpha|Q|{-}|V{\setminus}Q|, \alpha > 1$; in other words, $G'$ is a subgraph containing more nodes from $Q$ than other nodes. 
Discrepancy maximization is \NP-hard. 
On a similar line, the Center-piece subgraph problem (CEPS)~\citep{tong2006center} finds maximum weight subgraph that contains at least $k$ query nodes, at most $b$ other nodes. 
A generalization of the CEPS problem, the minimum Wiener connector problem (MWC)~\citep{ruchansky2015minimum} computes dense regions of a graph potentially representing community structures, given a set of nodes as input. MWC aims at finding a subgraph of $G$ induced by $Q$, denoted as $G[Q]$, that minimizes the sum of the pairwise distances among the nodes in $Q$, i.e, $\argmin_{G[Q]}\sum_{\{u,v\}{}\in{}Q}{}d_{G[Q]}(u,v)$.

Providing examples has also been used to detect communities~\citep{staudt2014detecting,perozzi2014focused}, where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node in $v \in Q$ as the only representative of a community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the 
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns cluster that better represent the seed nodes $Q$.
In addition, FocusCO returns outliers that do not belong to any community identified so far.

@@

%, where $\ell : V \cup E \to \mathcal{L}$ is a labelling function on a set of labels $\mathcal{L}$

\dnote{DAVIDE: Maybe to expand a bit more.}

@@

\noindent Graph exploration entails that a user provided query on a graph is indefinite in nature, and therefore is likely to return either too few or too-many results. 
For this reason query reformulation techniques aim at modifying the query to lead the user to the intended result~\citep{mottin2015graph,hurtado2008query,islam2015efficient}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$ with labeling function on nodes and edges $\ell$, is another query $Q'$ that is either a supergraph or a subgraph of $Q$, $Q' \subseteq Q$ or $Q' \supseteq Q$. 
Queries for reformulation are usually subgraph isomorphism queries~\cite{lee2012depth}.  
Therefore, $Q'$ can be more specific or more generic than $Q$. 
Query reformulation has been proposed for collections of graphs, or \emph{graph databases}, as well as large graphs. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

@@

\eetitle{Query reformulation in large graphs.}
Few works explicitly explore query reformulation large graphs.
Early attempts in this direction propose to enrich the SPARQL semantics with a \textsc{RELAX} clause that returns a set of reformulations following some predefined rules (such as expanding edges with a specific label)~\citep{hurtado2008query}.
In~\citep{arenas2014faceted} the SPARQL reformulations are extended to OWL logic, where the semantics of each reformulation is captured by the RDF taxonomy. 
The user can interactively select or unselect among the possible expansion of a query such that the navigation is consistent with the rules.

@@

\dnote{DAVIDE: Expand?}

@@

\eetitle{Why-not queries in graphs.}
Why-not queries additionally require the user to provide a set of missing answers from the results of $Q$, and the system proposes a new query $Q'$ returning those results and the fewer number of irrelevant results. 
The only work in this direction is~\cite{islam2015efficient}. 
In order to return the why-not queries, the maximum common subgraph (MCS) among the query $Q$ and the missing answers $\mathcal{D}^-$ is computed. The best query is found as $\argmin_Q'\in \mathcal{D}\Delta(Q',D^{-})$.

%\dnote{WHERE? Why-not on graphs\citep{islam2015efficient}}

% Given query results, and additional missing graphs, how to find the minimal query as close as possible to Q efficiently. Use a distance among queries.

%% SKYLINE? Do we add this? 
%\item Skyline queries~\cite{zheng2014efficient,zou2010dynamic}

% \eetitle{Missing-answers:}

>>>>

\noindent One of the earliest attempts to bring examples as a query method is query-by-example~\citep{zloof1975query}.
The main idea was to help the user in the query formulation, allowing her to specify the shape of the results in terms of templates for tuples, i.e., examples.
Query-by-example has been lately revisited, and the use of examples have found application in graph data. 
The definition of example has transformed from a mere template to the representative of the intended results the user would like to retrieve.
\emph{Examples} for a graph $G = (V,E)$ can be either \emph{set of nodes} $Q \subseteq V$, \emph{tuple} of nodes $(v_1, ..., v_n) \in V^n$, or \emph{subgraphs} $Q \subseteq G$, where with an abuse of notation $\subseteq$ indicates both set and structural inclusion.

\eetitle{Set of nodes as examples.} Several analyses can be performed when a set of examples nodes $Q\subseteq V$ is provided; this includes the discovery of dense graph regions~\citep{gionis2015bump,ruchansky2015minimum}, central nodes~\citep{tong2006center}, and communities~\citep{staudt2014detecting,perozzi2014focused}.%, and targeted graph summarization~\citep{zhang2010discovery}. 
Discrepancy maximization in graphs~\citep{gionis2015bump} aims at finding a connected subgraph $G' = (V', E'), G' \subseteq G$ that maximizes the discrepancy $\delta(G'){=}\alpha|Q|{-}|V{\setminus}Q|, \alpha > 1$; in other words, $G'$ is a subgraph containing more nodes from $Q$ than other nodes. 
Discrepancy maximization is \NP-hard. 
On a similar line, the Center-piece subgraph problem (CEPS)~\citep{tong2006center} finds the maximum weight subgraph that contains at least $k$ query nodes and at most $b$ other nodes. 
A generalization of the CEPS problem, the minimum Wiener connector problem (MWC)~\citep{ruchansky2015minimum} computes dense regions of a graph potentially representing community structures, given a set of nodes as input. MWC aims at finding a subgraph of $G$ induced by $Q$, denoted as $G[Q]$, that minimizes the sum of the pairwise distances among the nodes in $Q$, i.e, $\argmin_{G[Q]}\sum_{\{u,v\}{}\in{}Q}{}d_{G[Q]}(u,v)$.

Providing examples has also been used to detect communities~\citep{staudt2014detecting,perozzi2014focused}, where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node in $v \in Q$ as a representative of a different community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the 
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns cluster that better represent the seed nodes $Q$.
In addition, FocusCO returns outliers that do not belong to any community identified so far.

@@

%\dnote{DAVIDE: Maybe to expand a bit more.}

@@

\noindent Graph exploration entails that a user provided query on a graph is indefinite in nature, and therefore is likely to return either too few or too-many results. 
For this reason query reformulation techniques aim at modifying the query to lead the user to the intended result~\citep{mottin2015graph,hurtado2008query,islam2015efficient}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$ with labeling function on nodes and edges $\ell$, is another query $Q'$ that is either a supergraph or a subgraph of $Q$, $Q' \subseteq Q$ or $Q' \supseteq Q$. Therefore, $Q'$ can be more specific (supergraph) or more generic (subgraph) than $Q$. 
Queries considered in graph query reformulation are usually subgraph isomorphism queries~\cite{lee2012depth}.  
Query reformulation has been proposed for collections of graphs, or \emph{graph databases}, as well as large graphs. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

@@

\eetitle{Query reformulation in large graphs.}
Few works explicitly explore query reformulation large graphs.
Early attempts in this direction propose to enrich the SPARQL semantics with a \textsc{RELAX} clause that returns a set of reformulations following some predefined rules (such as expanding edges with a specific label)~\citep{hurtado2008query}.
In~\citep{arenas2014faceted} the SPARQL reformulations are extended to OWL logic, where the semantics of each reformulation is captured by the RDF taxonomy. 
The user can interactively accept or reject the possible expansions of a query such that the navigation is consistent with the rules.

@@

%\dnote{DAVIDE: Expand?}

@@

\eetitle{Why-not queries in graphs.}
Why-not queries additionally require the user to provide a set of missing answers from the results of $Q$, and the system proposes a new query $Q'$ returning those results and the fewer number of irrelevant results. 
The only work in this direction is~\cite{islam2015efficient}. 
In order to return the why-not queries, the maximum common subgraph (MCS) among the query $Q$ and the missing answers $\mathcal{D}^-$ is computed. The best query is found minimizing the maximum distance among $Q'$ and the missing answers $\mathcal{D}^-$ as $\argmin_{Q'\in \mathcal{D}} \max\{\Delta(Q',G)|G \in D^{-}\})$, where given $G_1 = (E_1,V_1, \ell_1), G_2 = (E_2,V_2, \ell_2)$, $\Delta(G_1, G_2) = |E_1| + |E_2| - 2 |\mathsf{MCS}(G_1,G_2)|$.

%% SKYLINE? Do we add this? 
% \eetitle{Skyline queries on graphs.}
% Skyline queries~\cite{zheng2014efficient,zou2010dynamic}

### 2017-11-12 paper.tex
Exp changed
Added preliminary on example-based methods
Added example-based methods
Added some comment
First complete version
Finished reformulation

\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage[normalem]{ulem}	% for strike-through of text with \sout{}  
\usepackage{hyperref}  %for hyperlinks
\usepackage{soul}   % for high-lighting of text
\usepackage{xspace}
\usepackage{enumitem}

@@

@@

Algorithms for graph exploration entail that the user is not able to completely specify the object of interest with  a structure query, such as SPARQL~\cite{prud2006sparql}, but rather expresses the need with simple, more ambiguous languages.

This asymmetry between the rigidity of the structured queries and the ambiguity of the user has inspired the study of approximate, flexible, and example-based methods.

@@

\stitle{Keyword Graph Queries} \dnote{DAVIDE: To add}

>>>>

\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage[normalem]{ulem}	% for strike-through of text with \sout{}  
\usepackage{hyperref}  %for hyperlinks
\usepackage{soul}   % for high-lighting of text
\usepackage{xspace}
\usepackage{enumitem} 		% For customizing lists
\usepackage{amsfonts}		% using of mathbb fonts
\usepackage{amsmath}
% \usepackage{amsthm}

@@

\DeclareMathOperator*{\argmax}{\arg\max}
\DeclareMathOperator*{\argmin}{\arg\min}

@@

Algorithms for graph exploration assume the user is not able to completely specify the object of interest with  a structured query, like a SPARQL~\cite{prud2006sparql} query, but rather expresses the need with a simpler, more ambiguous language.

This asymmetry between the rigidity of structured queries and ambiguity of the user has inspired the study of approximate, flexible, and example-based methods.

@@

\stitle{Keyword Graph Queries} \dnote{(Yinghui)}
